---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nuyina.envdata

<!-- badges: start -->
<!-- badges: end -->

The goal of nuyina.envdata is to copy satellite environmental data onto the Nuyina undwerway dataset. 

The data result is in this Parquet (the names of columns are likely to change). 

```
https://projects.pawsey.org.au/idea-objects/nuyina-envdata.parquet
```


So in R

```{r}
env <- arrow::read_parquet("https://projects.pawsey.org.au/idea-objects/nuyina-envdata.parquet")
names(env)  ## sst, sea ice, altimetry, various

get_underway <- function(x) {
  ## read the bulk
  d <- arrow::read_parquet("https://github.com/mdsumner/nuyina.underway/raw/main/data-raw/nuyina_underway.parquet")
  ## read the rest
  d1 <- tibble::as_tibble(vapour::vapour_read_fields("WFS:https://data.aad.gov.au/geoserver/ows?service=wfs&version=2.0.0&request=GetCapabilities",
                                                     sql = sprintf("SELECT * FROM \"underway:nuyina_underway\" WHERE datetime > '%s'",
                                                                   format(max(d$datetime, "%Y-%m-%dT%H:%M:%SZ")))))
  dplyr::bind_rows(d, d1)

}

## reads a cached Parquet and gets more recent rows from the geoserver
uwy <- get_underway()

(data <- dplyr::inner_join(env, uwy, "gml_id"))

## so now compare GHRSST with underway temp


plot(data$datetime, data$`ghrsst-tif_1`, pch = ".")
points(data$datetime, data$sea_water_temperature, pch = ".", col = "red")

```
We're running this on Pawsey with 

```
module load singularity/4.1.0-slurm


cd $MYSCRATCH/nuyina.envdata

singularity exec $MYSOFTWARE/sif_lib/gdal-builds_rocker-gdal-dev-python.sif   R CMD BATCH --no-restore --no-save  extract.R > run.Rout

```

Using 64 cores and reasonable memory this runs in under 5 minutes. We get OISST, GHRSST, AMSR sea ice (3.125km), NSIDC seaice (25km), and various altimetry products sla, adt, ugos, vgos. 


## Code of Conduct
  
Please note that the nuyina.envdata project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
